Quanta concentration and Transmission risk

### 2024-06-03 analysis/qctr.Rmd
Update modeling results

```{r illustration}
# data
mth <- 10
dy <- 25
sim <- 1
param_1025 <- readRDS(
  paste0(
    "simulations/", "/", "sim-param-",
    2021, "-", mth, "-", dy, ".rds"
  )
)
track_1025 <- readRDS(
  paste0(
    "simulations/", "/", "tracking-df-",
    250, "px-", 2021, "-", mth, "-", dy, ".rds"
  )
)
track_undiag <- track_1025 %>%
  dplyr::filter(tracking_end != "Possible HCW")
track_diag <- dplyr::filter(track_1025, is_infectious)
track_undiag <- dplyr::filter(
  track_undiag, !is_infectious | is.na(is_infectious)
)
track_tb_all <- rbind(
  track_diag,
  filter(
    track_undiag,
    patient_id %in% param_1025[[paste0("undiagTB", "_", "du")]][[sim]]
  )
)
aer_df <- readRDS("data-clean/environmental/air-change-rate.rds") %>%
  filter(
    month(date) == as.numeric(mth),
    day(date) == as.numeric(dy)
  )

@@

```{r}
main_tr <- main_tr %>%
  mutate(P_unc = P80 - P20)

hr_lu_pt <- main_tr %>%
  filter(P_unc < .25 / 100, P_mean > 0.25 / 100) %>%
  head(1)

main_focus_pl <- main_tr %>%
  ggplot(aes(x = P_unc, y = P_mean)) +
  geom_point(shape = 4) +
  annotate(
    "point",
    x = hr_lu_pt$P_unc,
    y = hr_lu_pt$P_mean,
    size = 7,
    shape = 1,
    color = "red"
  ) +
  annotate(
    geom = "segment",
    x = hr_lu_pt$P_unc + .00002,
    y = hr_lu_pt$P_mean + .0004,
    xend = hr_lu_pt$P_unc + .00008,
    yend = hr_lu_pt$P_mean + .004,
    arrow = arrow(length = unit(0.1, "cm")),
    color = "red"
  ) +
  annotate(
    geom = "text",
    x = hr_lu_pt$P_unc + .00008,
    y = hr_lu_pt$P_mean + .004,
    label = "Moderate risk,\nlow uncertainty",
    hjust = -.1,
    size = 6.5 / cm(1),
    color = "red"
  ) +
  scale_y_continuous(
    expand = expansion(mult = c(0.01, 0.01)),
    limits = c(0, .01),
    breaks = seq(0, .01, .0025),
    labels = function(x) round_k(100 * x, 3)
  ) +
  scale_x_continuous(
    expand = expansion(mult = c(0.01, 0.01)),
    limits = c(0, .002),
    breaks = seq(0, .002, .0005),
    labels = function(x) round_k(100 * x, 3)
  ) +
  labs(
    x = "Uncertainty (80%-CrI, pp)",
    y = "Mean risk of infection (%)"
  ) +
  theme_bw2() +
  theme(
    plot.title.position = "plot",
    plot.title = element_text(size = 10, face = 2),
    plot.margin = margin(.5, .5, .5, .5, "cm")
  )

save_plot(
  main_focus_pl,
  "results/modeling/patient-risk-focus-plot.png",
  w = 12,
  h = 10
)
```

@@

assoc_df <- track_ft %>%
  # left_join(
  #   aer %>%
  #     filter(room == "Waiting room") %>%
  #     dplyr::select(date, daytime, aer)
  # ) %>%
  mutate(patient_id = paste(
    lubridate::month(date),
    lubridate::day(date),
    patient_id,
    sep = "-"
  )) %>%
  left_join(
    main_tr %>%
      dplyr::select(patient_id, P_mean)
  )

@@

amod_est %>%
  group_by(variable) %>%
  summarize(
    lower = quantile(value, .025),
    mean = mean(value),
    upper = quantile(value, .975)
  ) %>%
  mutate(across(c(lower, mean, upper), ~ round_k(.x, 2)))
```

## Comparison with temporal model

```{r}
# files
files_temp <- list.files("simulations/temporal/",
  full.names = TRUE, pattern = "trans-risk",
  recursive = TRUE
)

temp_tr <- map_dfr(files_temp, average_trans_risk)
temp_annon <- annotate_average_trans_risk(temp_tr)

# comparison with temporal model
mod_comp <- left_join(
  temp_tr %>%
    dplyr::select(patient_id, P_mean) %>%
    rename(`Temporal model` = P_mean),
  main_tr %>%
    dplyr::select(patient_id, P_mean) %>%
    mutate(`Spatiotemporal model` = P_mean)
) %>%
  mutate(
    ratio = abs(`Spatiotemporal model` - `Temporal model`) / `Temporal model` * 100
  )

summary(mod_comp$ratio)
```

@@

# plot mean
mean_roi_comp_pl <- ggplot(
  tr_comp,
  aes(x = P_mean)
) +
  geom_histogram(
    mapping = aes(fill = P_col),
    binwidth = .0005,
    boundary = 1
  ) +
  geom_text(
    data = annon_comp,
    mapping = aes(x = Inf, y = Inf, label = lab),
    size = 8 / cm(1),
    hjust = 1, vjust = 2
  ) +
  facet_wrap(~scenario, ncol = 2) +
  scale_fill_manual(values = wes_palette("Darjeeling1")[c(2, 3, 1)]) +
  coord_cartesian(expand = FALSE) +
  scale_x_continuous(
    labels = function(x) x * 100,
    breaks = c(0, 0.001, 0.005, 0.01, 0.015, 0.02),
    limits = c(0, 0.02)
  ) +
  scale_y_sqrt(
    labels = scales::comma,
    breaks = c(0, 25, 100, 250, 500, 1000),
    limits = c(0, NA)
  ) +
  labs(
    x = "Risk of infection (%)",
    y = "Number of clinical attendees"
  ) +
  theme_custom() +
  theme(
    legend.position = "bottom",
    legend.title = element_blank(),
    legend.key.height = unit(.6, "cm"),
    legend.key.width = unit(.4, "cm"),
    strip.text = element_text(hjust = 0)
  )

>>>>

```{r illustration}
# data
mth <- 10
dy <- 25
sim <- 2
param_1025 <- readRDS(
  paste0(
    "simulations/", "/", "sim-param-",
    2021, "-", mth, "-", dy, ".rds"
  )
)
track_1025 <- readRDS(
  paste0(
    "simulations/", "/", "tracking-df-",
    250, "px-", 2021, "-", mth, "-", dy, ".rds"
  )
)
track_undiag <- track_1025 %>%
  dplyr::filter(tracking_end != "Possible HCW")
track_diag <- dplyr::filter(track_1025, is_infectious)
track_undiag <- dplyr::filter(
  track_undiag, !is_infectious | is.na(is_infectious)
)
track_tb_all <- rbind(
  track_diag,
  filter(
    track_undiag,
    patient_id %in% param_1025[[paste0("undiagTB", "_", "du")]][[sim]]
  )
)
aer_df <- readRDS("data-clean/environmental/air-change-rate.rds") %>%
  filter(
    month(date) == as.numeric(mth),
    day(date) == as.numeric(dy)
  )

@@

@@

assoc_df <- track_ft %>%
  mutate(patient_id = paste(
    lubridate::month(date),
    lubridate::day(date),
    patient_id,
    sep = "-"
  )) %>%
  left_join(
    main_tr %>%
      dplyr::select(patient_id, P_mean)
  )

@@

amod_est %>%
  group_by(variable) %>%
  summarize(
    lower = quantile(value, .025),
    mean = mean(value),
    upper = quantile(value, .975)
  ) %>%
  mutate(across(c(lower, mean, upper), ~ round_k(.x, 2))) %>%
  dplyr::select(variable, mean, lower, upper)
```

@@

# plot mean
mean_roi_comp_pl <- ggplot(
  tr_comp,
  aes(x = P_mean)
) +
  geom_histogram(
    mapping = aes(fill = P_col),
    binwidth = .0005,
    boundary = 1
  ) +
  geom_text(
    data = annon_comp,
    mapping = aes(x = Inf, y = Inf, label = lab),
    size = 8 / cm(1),
    hjust = 1, vjust = 2
  ) +
  facet_wrap(~scenario, ncol = 2, scales = "free_x") +
  scale_fill_manual(values = wes_palette("Darjeeling1")[c(2, 3, 1)]) +
  coord_cartesian(expand = FALSE) +
  scale_x_continuous(
    labels = function(x) x * 100,
    breaks = c(0, 0.001, 0.005, 0.01, 0.015, 0.02),
    limits = c(0, 0.02)
  ) +
  scale_y_sqrt(
    labels = scales::comma,
    breaks = c(0, 25, 100, 250, 500, 1000),
    limits = c(0, NA)
  ) +
  labs(
    x = "Risk of infection (%)",
    y = "Number of clinical attendees"
  ) +
  theme_custom() +
  theme(
    legend.position = "bottom",
    legend.title = element_blank(),
    legend.key.height = unit(.6, "cm"),
    legend.key.width = unit(.4, "cm"),
    strip.text = element_text(hjust = 0),
    panel.spacing = unit(.5, "cm")
  )
